---
title: "Visualizations for Google Portfolio Project 1"
author: "George R. Yang"
date: "2022-08-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary

For the Google UX Design course, I designed a music streaming tracker app that included some placeholder visualizations showing the total number of streams of unique listeners over time. This test code attempts to recreate the visualizations that were originally created in Figma using some made-up data.


## Load Packages
``` {r load_packages}
library(tidyverse)
library(readxl)
library(ggchicklet)
library(showtext)
```

## Load and Clean Data
```{r load_data}
# Load data
song_data <- read_excel("song_data.xlsx", sheet = 1)

# Clean data

## All streaming data
song_streams <- song_data %>%
  select(streams_202201:streams_202208) %>%
  summarize(
    Jan = sum(streams_202201),
    Feb = sum(streams_202202),
    Mar = sum(streams_202203),
    Apr = sum(streams_202204),
    May = sum(streams_202205),
    Jun = sum(streams_202206),
    Jul = sum(streams_202207),
    Aug = sum(streams_202208)
  ) %>%
  pivot_longer(everything(), names_to = "time", values_to = "streams") %>%
  mutate(time = fct_relevel(time,  c(
    "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug"
  ))) 

## 火 streaming data
huo_streams <- song_data %>%
  filter(song == "火") %>%
  select(streams_202201:streams_202208) %>%
  rename(
    Jan = streams_202201,
    Feb = streams_202202,
    Mar = streams_202203,
    Apr = streams_202204,
    May = streams_202205,
    Jun = streams_202206,
    Jul = streams_202207,
    Aug = streams_202208
  ) %>%
  pivot_longer(everything(), names_to = "time", values_to = "streams") %>%
  mutate(time = fct_relevel(time,  c(
    "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug"
  )))

## 火 listener data
huo_listeners <- song_data %>%
  filter(song == "火") %>%
  select(listeners_202201:listeners_202208) %>%
  rename(
    Jan = listeners_202201,
    Feb = listeners_202202,
    Mar = listeners_202203,
    Apr = listeners_202204,
    May = listeners_202205,
    Jun = listeners_202206,
    Jul = listeners_202207,
    Aug = listeners_202208
  ) %>%
  pivot_longer(everything(), names_to = "time", values_to = "listeners") %>%
  mutate(time = fct_relevel(time,  c(
    "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug"
  )))

```

## Load Font
``` {r}
# Might not be working

font_add_google("Open Sans", "Open Sans")
showtext_auto()
```

## Create Summary Plot on Home Screen

```{r create_summary_plot}
# Create ggplot
song_sum_plot <- song_streams %>%
  ggplot(aes(time, streams)) +
  geom_chicklet(radius = unit(3, "mm"), fill = "#B56576") +
  labs(title = paste0(last(song_streams$streams) / 1000, "k"),
       subtitle = "streams") +
  theme_void() +
  theme(
    axis.text.x = element_text(color = "#355070", size = 14),
    panel.background = element_rect(fill = "#F0F0F0", color = "#F0F0F0"),
    plot.background = element_rect(fill = "#F0F0F0", color = "#F0F0F0"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    plot.title = element_text(
      face = "bold",
      color = "#355070",
      size = 32,
      hjust = 0,
      vjust = -3
    ),
    plot.subtitle = element_text(
      color = "#355070",
      size = 16,
      hjust = 0,
      vjust = -5
    )
  )

# Show plot
song_sum_plot
```

## Create Streams and Listeners Plots on Song Details Screen for Most Recent Song

### Streams Plot for Most Recent Song
```{r create_streams_plot}
# Create streams plot
huo_streams_plot <- huo_streams %>%
  ggplot(aes(time, streams)) +
  geom_chicklet(radius = unit(3, "mm"), fill = "#B56576") +
  theme_void() +
  theme(
    axis.text.x = element_text(color = "#355070", size = 14),
    panel.background = element_rect(fill = "#F0F0F0", color = "#F0F0F0"),
    plot.background = element_rect(fill = "#F0F0F0", color = "#F0F0F0"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
   )

# Show streams plot
huo_streams_plot
```

### Listeners Plot for Most Recent Song
```{r create_listeners_plot}
# Create listeners plot
huo_listeners_plot <- huo_listeners %>%
  ggplot(aes(time, listeners)) +
  geom_chicklet(radius = unit(3, "mm"), fill = "#6D597A") +
  theme_void() +
  theme(
    axis.text.x = element_text(color = "#355070", size = 14),
    panel.background = element_rect(fill = "#F0F0F0", color = "#F0F0F0"),
    plot.background = element_rect(fill = "#F0F0F0", color = "#F0F0F0"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
   )

# Show listeners  plot
huo_listeners_plot
```

## Save Plots as Images

```{r save_plots}
ggsave(song_sum_plot, file = "01_song_sum_plot.png")
ggsave(huo_streams_plot, file = "02_huo_streams_plot.png")
ggsave(huo_listeners_plot, file = "03_huo_listeners_plot.png")
```